Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-16 ms.qmd
Need to think about how to deal with RE in predictions. They explain a lot of variation, do we integrate the unique data such that they go across all random effects?

######################################################################
# Model predcitions for terrestrial, marine and freshwater ectotherms
######################################################################
# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.

## Terrestrial Ectotherms
  terrest_data <- sub_data  %>% filter(habitat == "t")
    new_data_t <- data.frame(
      spp = terrest_data$spp,
      trait = terrest_data$trait,
      habitat = terrest_data$habitat,
      c_accl_time = 0,
      V = 0,
      lat = terrest_data$lat.y,
      long = terrest_data$long.x
    )

terre_pred <- predict(model5_bayes, newdata = new_data_t, summary = FALSE)

>>>>

######################################################################
# Model predcitions for terrestrial, marine and freshwater ectotherms
######################################################################
# Now we need to make predictions for new data. We first need to create new data. We need to do this for each habitat type because they are all a little different. Lets do terrestrial first.
test <- sub_data  %>% filter(habitat == "t") %>% distinct(spp, lat.y, long.x)
length(unique(test$spp))

## Terrestrial Ectotherms
  terrest_data <- sub_data  %>% filter(habitat == "t")  %>% distinct(spp, habitat, lat.y, long.x)
  new_data_t <- data.frame(
      c_accl_time = 0,
      V = 0,
      trait = 0,
      obs = 0, 
      type = "acute",
      record_num = 0,
      species_full = terrest_data$spp
    )

  # Create new dataframe with only unique values for predcition.
  new_data_t2  <- cbind(terrest_data, new_data_t)

  # We'll now make the predcitions from the model object using the new dataframe
  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, robust = FALSE)

  # Test manual calculations. We can also set summary = FALSE and then do the calculations ourselves. Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE  
  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, robust = FALSE)
  plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))
